### 2023-03-17 main.tex
Added \newpage command to ensure page counter is not set for TOC
Changed figure command to use chapter.fignum style
Added chapter 2 appendix
Added title

% Chapter and figure formatting
\usepackage{titlesec}  % Modify chapter title format
\titleformat{\chapter}[display]% Shape (chapter label in separate paragraph)
                      {\bfseries\Large}% Format
                      {\MakeUppercase{\chaptertitlename} \thechapter}% Label
                      {0in}% Sep
                      {}% Before code
                      []% After code
\setcounter{tocdepth}{1}  % Only number divisions to section
\usepackage[labelfont=bf, labelsep=period]{caption}
\renewcommand{\figurename}{Fig}

@@

\begin{titlepage}
\begin{center}
    My long and grand sounding dissertation title\\
    \bigskip
    By\\
    Marc Singleton\\
    \vfill
    A dissertation submitted in partial satisfaction of the\\
    requirements for the degree of\\
    Doctor of Philosophy\\
    in\\
    Biophysics\\
    in the\\
    Graduate Division\\
    of the\\
    University of California, Berkeley\\
    \vfill
    Committee in charge:\\
    Professor Mike Eisen, Chair\\
    Professor Liana Lareau\\
    Professor Susan Marqusee\\
    Professor Priya Moorjani\\
    \bigskip
    Spring 2023\\
\end{center}
\end{titlepage}

@@

\setcounter{page}{1}  % Reset page counter after copyright
\begin{center}
    Abstract\\
    \bigskip
    My long and grand sounding dissertation title\\
    by\\
    Marc Singleton\\
    \bigskip
    Doctor of Philosophy in Biophysics\\
    University of California, Berkeley\\
    Professor Mike Eisen, Chair\\
    \bigskip
\end{center}
Here's the text for my abstract!
\clearpage

@@

\tableofcontents

\setcounter{chapter}{-1}  % Set chapter counter to 0
\chapter{Introduction}
\graphicspath{{chapter0/figures/}}
\setcounter{page}{1}  % Reset page counter after pre-main content
\pagenumbering{arabic}  % Set numbering style to arabic for main content
\input{chapter0/chapter0.tex}

@@

\chapter{Supporting information for chapter 3}
\label{appendix:b}
\setlength{\promptwidth}{0in}  % No indent for appendix code
\input{chapter3/training_tutorial_supporting.tex}

>>>>

% Chapter and figure formatting
\usepackage{titlesec}  % Modify chapter title format
\titleformat{\chapter}[display]% Shape (chapter label in separate paragraph)
                      {\bfseries\Large}% Format
                      {\MakeUppercase{\chaptertitlename} \thechapter}% Label
                      {0in}% Sep
                      {}% Before code
                      []% After code
\setcounter{tocdepth}{1}  % Only number divisions to section
\usepackage[labelfont=bf, labelsep=period]{caption}
\renewcommand{\thefigure}{\thechapter.\arabic{figure}}

@@

\begin{titlepage}
\begin{center}
    Finding structure in disorder: Evolutionary analyses of disordered proteins in \textit{Drosophila}\\
    \bigskip
    By\\
    Marc Singleton\\
    \vfill
    A dissertation submitted in partial satisfaction of the\\
    requirements for the degree of\\
    Doctor of Philosophy\\
    in\\
    Biophysics\\
    in the\\
    Graduate Division\\
    of the\\
    University of California, Berkeley\\
    \vfill
    Committee in charge:\\
    Professor Mike Eisen, Chair\\
    Professor Liana Lareau\\
    Professor Susan Marqusee\\
    Professor Priya Moorjani\\
    \bigskip
    Spring 2023\\
\end{center}
\end{titlepage}

@@

\setcounter{page}{1}  % Reset page counter after copyright
\begin{center}
    Abstract\\
    \bigskip
    Finding structure in disorder: Evolutionary analyses of disordered proteins in \textit{Drosophila}\\
    by\\
    Marc Singleton\\
    \bigskip
    Doctor of Philosophy in Biophysics\\
    University of California, Berkeley\\
    Professor Mike Eisen, Chair\\
    \bigskip
\end{center}
Here's the text for my abstract!
\clearpage

@@

\tableofcontents
\newpage  % End page so numbering is set properly
\setcounter{chapter}{-1}  % Set chapter counter to 0
\setcounter{page}{1}  % Reset page counter after pre-main content
\pagenumbering{arabic}  % Set numbering style to arabic for main content

\chapter{Introduction}
\graphicspath{{chapter0/figures/}}
\input{chapter0/chapter0.tex}

@@

\chapter{Supporting information for chapter 2}
\label{appendix:b}
\graphicspath{{chapter2/figures/}}
\input{chapter2/chapter2_supporting.tex}

\chapter{Supporting information for chapter 3}
\label{appendix:c}
\setlength{\promptwidth}{0in}  % No indent for appendix code
\input{chapter3/training_tutorial_supporting.tex}
